GeckoGraph: A Visual Language for Polymorphic Types

### 2025-10-26 response.tex

\paragraph{Removed unused figure} We removed the previous Figure~4, as it did not contribute additional information to the paper.

\paragraph{Cosmetic and consistency edits} Grammar, spelling, LaTeX syntax, and stylistic consistency have been carefully reviewed and corrected throughout the manuscript.
\section{Detailed Responses to Reviewers}

\subsection*{Response to Reviewer 1}

\pointRaised{Comment 1:}{(Abstract, Introduction, Conclusion – Major) The manuscript’s tone in the Abstract and Conclusion appears overly strong given the presented evidence.}

\reply We appreciate this observation. The language in the \textit{Abstract}, \textit{Introduction}, and \textit{Conclusion} has been moderated to ensure that claims are proportionate to the results. The revised version now presents both the positive and negative aspects of our findings.

\pointRaised{Comment 2:}{(Overall) The term “game” used to describe the user study could be misleading.}

@@

\reply We agree. The tasks in our study do not fully meet the criteria for a “game.” We now describe it more accurately as a “gamified user study” or simply a “user study,” emphasizing its educational and experimental nature.

\pointRaised{Comment 3:}{(Section 3.1) Clarify the explanation of type classes.}

@@

\reply The subsection on type classes (Section~3.1) has been rewritten for clarity and supported by clearer examples. Figure~3 has also been improved to include illustrative examples that reinforce our description of GeckoGraph.

\pointRaised{Comment 4:}{(Section 3) Clarify the syntactic sugar of curried functions.}

\reply We now explicitly clarify that the function notation \texttt{a -> b -> c} desugars to \texttt{a -> (b -> c)}, which is consistently represented in GeckoGraph.

\pointRaised{Comment 5:}{(Section 3) Figure 3: The second higher-order function type {\tt ((a -> b) -> b)} is tagged as binary but is unary.}

\reply We agree that the previous figure was confusing. Figure~4 (previously Figure~3) has been simplified for readability.

\pointRaised{Comment 6:}{(Section 3) Issues with figures and references.}

\reply The previous Figure~4 has been removed. Incorrect cross-references such as “Fig.~2.2” have been corrected (now “Fig.~8”), and redundant phrases like “Appendix Appendix~A” have been fixed.

\pointRaised{Comment 7:}{(Section 5) Temper the narrative of qualitative results—the data show neutral user opinions.}

\reply We have clarified that participants’ feedback was overall neutral. Descriptors such as “slightly positive” and “moderately negative” are now used to reflect sentiment values more precisely.

\pointRaised{Comment 8:}{(Section 6) Clarify speculative claims in the Discussion.}

\reply We now explicitly mark speculative interpretations in Section~6 (\textit{Discussion}) using leading phrases such as “We hypothesize that...”.

\pointRaised{Comment 9:}{(Overall) Wording and grammar issues.}

\reply We have corrected numerous stylistic and grammatical issues, including:
“expressiveness power” → “expressiveness”,
“high-order function” → “higher-order function,”
and “GechoGraph” → “GeckoGraph.”  
Unclear expressions such as “tangibly” and “regular higher-order function” have been revised or replaced with precise terms, and unnecessary spaces before footnotes have been removed.

@@

\subsection*{Response to Reviewer 2}

\pointRaised{Comment 1:}{(Section 1) Add a concluding paragraph in the Introduction describing the article’s organization.}

\reply We agree. A short paper-structure overview has been added at the end of Section~1 to guide the reader through the paper’s organization.

\pointRaised{Comment 2:}{(Section 2) The paper lacks sufficient background on type systems in functional languages.}

@@

\reply We have added a new section titled \textit{Type Systems in Functional Languages} immediately after the \textit{Introduction}. This section introduces key theoretical concepts and motivates the design rationale for GeckoGraph.

\pointRaised{Comment 3:}{(Section 3) The paper’s flow between subsections feels abrupt.}

\reply We have added a transitional paragraph between the \textit{Design Goals} and \textit{Detailed GeckoGraph Features} subsections in Section~3 to improve narrative flow.

\pointRaised{Comment 4:}{(Section 4) Clarify user tasks and results in Figures 9 and 10.}

\pointRaised{Comment 5:}{(Section 4) Clarify whether participants indicate their experience once or before each run.}

\pointRaised{Comment 6:}{(Section 4) Add reference for “between-subject design.”}

\reply We now correctly cite Fisher, R.A. \textit{The Design of Experiments} for the phrase “between-subject design.”

\pointRaised{Comment 7:}{(Section 6) The Discussion section is abstract and lacks concrete examples.}

@@

\reply We now correctly cite Fisher, R.A. \textit{The Design of Experiments} for the phrase “between-subject design.”

\pointRaised{Comment 7:}{(Section 6) The Discussion section is abstract and lacks concrete examples.}

\reply We have revised the \textit{Discussion} section to include additional examples illustrating practical applications of GeckoGraph. Figure~14 has been added to support this discussion.

\pointRaised{Comment 8:}{(Section 6 and 7) Begin Sections~6 (“Discussion”) and~7 (“Related Work”) with overview paragraphs explaining purpose and structure.}

\reply Overview paragraphs have been added at the start of both sections to help orient readers and clarify their organization.

\pointRaised{Comment 9:}{(Section 7) The Related Work section could benefit from additional references and a clearer structure.}

\reply We have expanded and reorganized the \textit{Related Work} section, including new references such as “Just TYPEical: Visualizing Common Function Type Signatures in R.” A short overview paragraph now outlines the section’s focus and structure.

\pointRaised{Comment 10:}{(Section 6) Distinguish between empirical findings and interpretations in the Discussion.}

\reply We now explicitly distinguish between observed results and speculative interpretations in the \textit{Discussion}, using phrases such as “We hypothesize that...” to signal interpretive commentary.

\pointRaised{Comment 11:}{(Overall) Usage of figures—some captions too long, Figure~4 unclear.}

\reply Figure captions throughout the paper have been shortened for conciseness. The previous Figure~4, which did not add new insight, has been removed.

\pointRaised{Comment 12:}{(Overall) Minor wording and grammar issues.}

\reply The manuscript has been thoroughly proofread for grammar, formatting, and coherence.  
Examples include corrected figure references (e.g., “Fig.~2.2” → “Fig.~8”), removal of redundant text (“Appendix Appendix~A” → “Appendix~A”), and clarification of unclear terms such as “approximity” and “during type errors.”

### 2025-10-26 main.tex
Final updates

{\bf Type inference}, or implicit typing, reduces the need for explicit type annotations by allowing the compiler to deduce types automatically.
Most modern languages employ some level of inference. For instance, Java’s var keyword (introduced in version 10) infers variable types at compile time based on their assigned values \cite{Java_Developers2023-an}, saving programmers from writing redundant type declarations, such as \textit {Car car = new Car()}.

@@

Curried functions are functions that return other functions (e.g. \texttt{ a -> (b -> c)}). In functional languages, they are often written with a syntactic shorthand, such as \texttt{ a -> b -> c}). These two forms are uniquely represented in GeckoGraph as two functions cells merged together \includegraphics[height=1em]{figures/Curry.png}. It appears as if the second function covers the right half of the first function, indicating that the second function is the return type of the first. Regular high-order functions (e.g., \texttt{(a -> b) -> c}) follow the rules of functions and nested data types \includegraphics[height=1.2em]{figures/HOF.png}. The placement of function indicators aims to make it easy to find desired functions in the documentation site based on function arity and higher-order functions (design goal \ref{goal3}). It is easy to tell high-order functions from the vertical position of the function indicators. Similarly, it is easy to count the arity of a function by counting the number of function indicators at the outer layer. For example, in Fig. \ref{fig:indicator}, the outer layer function indicators (the ones colored in the lightest shade of gray) suggest a ternary function. The two argument types and the return type are all functions.

\begin{figure}[h]
  \includegraphics[width=\linewidth]{figures/Indicator}
  \caption{
        \label{fig:indicator}
        An example of the visual hierarchy of the function indicator. The function indicator can be used to easily identify the arity of a function type by counting the connecting function indicators. For higher-order functions where functions are arguments or return values of other functions, it is very easy to see the ``level" of functions. 
  }
\end{figure}

>>>>

{\bf Type inference}, or implicit typing, reduces the need for explicit type annotations by allowing the compiler to deduce types automatically.
Most modern languages employ some level of inference. For instance, Java’s var keyword (introduced in version 10) infers variable types at compile time based on their assigned values \cite{Java-Developers2023-sp}, saving programmers from writing redundant type declarations, such as \textit {Car car = new Car()}.

@@

Curried functions are functions that return other functions (e.g. \texttt{ a -> (b -> c)}). In functional languages, they are often written with a syntactic shorthand, such as \texttt{ a -> b -> c}). These two forms are uniquely represented in GeckoGraph as two functions cells merged together \includegraphics[height=1em]{figures/Curry.png}. It appears as if the second function covers the right half of the first function, indicating that the second function is the return type of the first.  Higher-order functions that take other functions as arguments  (e.g., \texttt{(a -> b) -> c}) follow the rules of functions and nested data types \includegraphics[height=1.2em]{figures/HOF.png}. The placement of function indicators aims to make it easy to find desired functions in the documentation site based on function arity and higher-order functions (design goal \ref{goal3}). It is easy to tell high-order functions from the vertical position of the function indicators. Similarly, it is easy to count the arity of a function by counting the number of function indicators at the outer layer. For example, in Fig. \ref{fig:indicator}, the outer layer function indicators (the ones colored in the lightest shade of gray) suggest a ternary function. The two argument types and the return type are all functions.

\begin{figure}[h]
  \includegraphics[width=0.6\linewidth]{figures/Indicator.png}
  \caption{
        \label{fig:indicator}
        An example of the visual hierarchy of the function indicator. The function indicator can be used to easily identify the arity of a function type by counting the connecting function indicators.
  }
\end{figure}
